Teaching Dossier

### 2019-11-22 CUT/teaching-philosophy.tex
preamble to detailed feedback from report 2

\paragraph{Aspects to Maintain}

@@

\end{document}

>>>>

Caelan's general impression of the lesson can be summarized as ``\emph{You were confident, clear, and
knowledgeable in the classroom. Overall, your lesson was definitely a success}.''. As with the previous report, more detailed feedback was separated into aspects to maintain and targets for change. The relevant sections of the full report can be found in Appendix \ref{sec:observation-report-2}
\paragraph{Aspects to Maintain}

@@

\section{Teaching Observation Report 2}\label{sec:observation-report-2}
\end{document}
